Performance of two different ontological and data access methods

### 2014-07-10 cold2014/magnus.tex
move table 1
git-svn-id: https://svn.ifi.uio.no/repos/users/kjekje-phd@746 43ef1190-90fd-4dd7-a769-d0121f02b80e
move table 2
git-svn-id: https://svn.ifi.uio.no/repos/users/kjekje-phd@747 43ef1190-90fd-4dd7-a769-d0121f02b80e
move table 3
git-svn-id: https://svn.ifi.uio.no/repos/users/kjekje-phd@748 43ef1190-90fd-4dd7-a769-d0121f02b80e
see if we can tolerate figure 1 as is
git-svn-id: https://svn.ifi.uio.no/repos/users/kjekje-phd@749 43ef1190-90fd-4dd7-a769-d0121f02b80e

To evaluate the graphs we have used a method in the \textsf{FrF2} R
package called \textsf{DanielPlot} to create half-normal plots. The
intuition behind this is simple: If errors are normally distributed,
which is a conservative assumption, and there are no significant
effects they will also be normally distributed, and so the estimated
effects would end up on a straight line. Any significant deviations
from a straight line indicates a significant factor. That we use a
half-normal plot (rather than a normal plot) means that
the most significant effects will end up in the top right
corner. The axes themselves are not important to understand the plot
nor the results, refer to \cite{PlanExp} for details.  We have also
set the significance level at $\alpha = 0.05$, where
\textsf{DanielPlot} is using Lenth's method for the analysis of
unreplicated factorials.

@@

\begin{wraptable}{l}{0.35\textwidth}
    \begin{tabular}{ | l | l |}
    \hline
    {\bf Factor} & {\bf Abbrev} \\ \hline
   Ontology & \textsf{O} \\
   Fuel Type & \textsf{FT} \\
   Transmission & \textsf{T} \\
   Weight & \textsf{W} \\
   Total Weight & \textsf{WT} \\
   Emission & \textsf{E} \\
   \# of Gears & \textsf{G} \\
   Seating Capacity & \textsf{SC} \\
   Fuel Consumption & \textsf{FC} \\
   Doors & \textsf{D} \\
\hline
    \end{tabular}
\caption{Factors and their abbreviation}\label{facandabbrev}
\end{wraptable}

@@

The next step was to create the planning matrix for this
experiment. Table~\ref{3factor} shows all the 8 runs for the
experiment with three factors.  After each run the response time were
logged to that particular run. The response time were then used to
check for significant effect when the experiment were evaluated
\begin{wraptable}{l}{0.67\textwidth}
    \begin{tabular}{ | l | l l l |}
    \hline
    {\bf Run} & {\bf Ontology} & {\bf Fuel type} & {\bf Transmission} \\ \hline
	1 & -vso & Diesel & Automatic Gearbox \\ \hline 
	2 & -co & Diesel & Automatic Gearbox \\ \hline 
	3 & -vso & Unleaded Petrol & Automatic Gearbox \\ \hline 
	4 & -co & Unleaded Petrol & Automatic Gearbox \\ \hline 
	5 & -vso & Diesel & Manual Gearbox \\ \hline 
	6 & -co & Diesel & Manual Gearbox \\ \hline 
	7 & -vso & Unleaded Petrol & Manual Gearbox \\ \hline 
	8 & -co & Unleaded Petrol & Manual Gearbox \\ \hline 
    \end{tabular}
    \caption{Planning matrix for experiment with three factors and
      their levels.}\label{3factor}
\end{wraptable}

@@

\begin{wraptable}{l}{0.25\textwidth}
%\vspace{-25pt}
    \begin{tabular}{ | l l |}
    \hline
    {\bf Factors} & {\bf Effect}  \\ \hline
	  O     & 2.246\\ \hline
	  O:T    &0.454 \\ \hline
	  O:FT:T &0.453 \\ \hline
	  T      &0.451 \\ \hline
	  FT:T   &0.450 \\ \hline
	  O:FT   &0.124 \\ \hline
	  FT     &0.118 \\ \hline
    \end{tabular}
\caption{Table of absolute effects for the three factor experiment}\label{3factorEffect}
%\vspace{-25pt}
\end{wraptable}

\begin{wrapfigure}{l}{0.65\textwidth}
 \includegraphics[width=8.5cm, height=7cm]{2factorfinal.pdf}
  \caption{Resulting graph for the three factor experiment}\label{3factorGraph}
\end{wrapfigure}

@@

In the graph~\ref{10factorGraph} we can see the results from running
all the 1024 runs.  We can see that there are a lot of significant
effects present here. 
Unfortunately there are so many significant factors that there are
some of them that are illegible, but most of them have a low impact on
the significance graph.  In Table~\ref{10factorEffect} we can see the top
fifteen absolute effects. We can see that emission and fuel consumption are 
the most significant factors besides the ontology factor.
The linear model again tells us that the option
\textsf{-vso} has a significantly lower response time than
\textsf{-co}.

>>>>

To evaluate the graphs we have used a method in the \textsf{FrF2} R
package called \textsf{DanielPlot} to create half-normal plots. The
intuition behind this is simple: If errors are normally distributed,
which is a conservative assumption, and there are no significant
effects they will also be normally distributed, and so the estimated
effects would end up on a straight line. Any significant deviations
from a straight line indicates a significant factor.  That we use a
half-normal plot (rather than a normal plot) means that
the most significant effects will end up in the top right
corner. 
%
\begin{wraptable}{r}{0.35\textwidth}
\vspace{-35pt}
    \begin{tabular}{ | l | l |}
    \hline
    {\bf Factor} & {\bf Abbrev} \\ \hline
   Ontology & \textsf{O} \\
   Fuel Type & \textsf{FT} \\
   Transmission & \textsf{T} \\
   Weight & \textsf{W} \\
   Total Weight & \textsf{WT} \\
   Emission & \textsf{E} \\
   \# of Gears & \textsf{G} \\
   Seating Capacity & \textsf{SC} \\
   Fuel Consumption & \textsf{FC} \\
   Doors & \textsf{D} \\
\hline
    \end{tabular}
\caption{Factors and their abbreviation}\label{facandabbrev}
\vspace{-45pt}
\end{wraptable}
%
The axes themselves are not important to understand the plot
nor the results, refer to \cite{PlanExp} for details.  We have also
set the significance level at $\alpha = 0.05$, where
\textsf{DanielPlot} is using Lenth's method for the analysis of
unreplicated factorials.

@@

@@

The next step was to create the planning matrix for this
experiment. Table~\ref{3factor} shows all the 8 runs for the
experiment with three factors.  After each run the response time were
logged to that particular run. The response time were then used to
check for significant effect when the experiment was evaluated.

\begin{wraptable}{r}{0.67\textwidth}
\vspace{-20pt}
    \begin{tabular}{ | l | l l l |}
    \hline
    {\bf Run} & {\bf Ontology} & {\bf Fuel type} & {\bf Transmission} \\ \hline
	1 & -vso & Diesel & Automatic Gearbox \\ \hline 
	2 & -co & Diesel & Automatic Gearbox \\ \hline 
	3 & -vso & Unleaded Petrol & Automatic Gearbox \\ \hline 
	4 & -co & Unleaded Petrol & Automatic Gearbox \\ \hline 
	5 & -vso & Diesel & Manual Gearbox \\ \hline 
	6 & -co & Diesel & Manual Gearbox \\ \hline 
	7 & -vso & Unleaded Petrol & Manual Gearbox \\ \hline 
	8 & -co & Unleaded Petrol & Manual Gearbox \\ \hline 
    \end{tabular}
    \caption{Planning matrix for experiment with three factors and
      their levels.}\label{3factor}
\vspace{-20pt}
\end{wraptable}

@@

\begin{wraptable}{l}{0.25\textwidth}
\vspace{-35pt}
    \begin{tabular}{ | l l |}
    \hline
    {\bf Factors} & {\bf Effect}  \\ \hline
	  O     & 2.246\\ \hline
	  O:T    &0.454 \\ \hline
	  O:FT:T &0.453 \\ \hline
	  T      &0.451 \\ \hline
	  FT:T   &0.450 \\ \hline
	  O:FT   &0.124 \\ \hline
	  FT     &0.118 \\ \hline
    \end{tabular}
\caption{Table of absolute effects for the three factor experiment}\label{3factorEffect}
\vspace{-15pt}
\end{wraptable}

@@

In Figure~\ref{10factorGraph} we can see the results from running
all the 1024 runs.  We can see that there are a lot of significant
effects present here. 
Unfortunately there are so many significant factors that there are
some of them that are illegible, but most of them have a low impact on
the significance graph.  In Table~\ref{10factorEffect} we can see the top
fifteen absolute effects. We can see that emission and fuel consumption are 
the most significant factors besides the ontology factor.
The linear model again tells us that the option
\textsf{-vso} has a significantly lower response time than
\textsf{-co}.

\begin{figure}%{r}{0.65\textwidth}
\begin{center}
\vspace{-15pt}
 \includegraphics[width=8.5cm, height=7cm]{2factorfinal.pdf}
  \caption{Resulting graph for the three factor experiment}\label{3factorGraph}
\vspace{-10pt}
\end{center}
\end{figure}
